Behavior Driven Development in Haskell

### 2012-06-02 paper.tex
Terminology
Wording

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertions} in xUnit
    testing frameworks, but use a different terminology.

@@

Haddock has markup support for code blocks, and they are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt filepath} package.

>>>>

\item[expectation]
    Expectations are used to define the expected outcome of a code
    example.  They serve the same purpose as \emph{assertions} in
    traditional unit testing frameworks, but use a different
    terminology.

@@

Haddock has markup support for code blocks, and code blocks are widely used
to include properties and examples into documentation\footnote{
See e.g. the documentation of
{\tt containers},
{\tt filepath},
{\tt bytestring} or
{\tt text}}.
Here is an example from the {\tt filepath} package.
